---
title: "purr & functions exploration"
output: 
  html_notebook:
    theme: spacelab
    highlight: tango
    df_print: paged
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    number_sections: true
    toc_depth: 6
---


<style type="text/css">

body, td {
   font-family: "OCR-B 10 BT";
}
code.r{
  font-family: "OCR-B 10 BT";
}
pre {
  font-family: "OCR-B 10 BT";
}
</style>



# Exploring purr functions

from: 

http://www.rebeccabarter.com/blog/2019-08-19_purrr/

https://adv-r.hadley.nz/functionals.html#purrr-style

## options & settings

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
options(scipen = 999)
```


## Libs

```{r}
library(tidyverse)
```


## gapminder data

```{r}
# to download the data directly:

gapminder_orig <- read.csv("https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/gh-pages/_episodes_rmd/data/gapminder-FiveYearData.csv")

# define a copy of the original dataset that we will clean and play with 
gapminder <- gapminder_orig
```


```{r}
head(gapminder)
```

```{r}
names(gapminder)
```

```{r}
dim(gapminder)
```

## map & modify from purr

### class

```{r}
class(gapminder$country)
```


```{r}
gapminder %>% map_chr(class)
```

```{r}
gapminder %>% modify(class)
```

`modify()` returns in the same output format as input, so it is not a suitable choice in this case


### n_distinct

```{r}
gapminder %>% map_dbl(n_distinct)
```

### class + n_distinct

```{r}
gapminder %>% map_df(~data.frame(class = class(.x),
                                 distinct = n_distinct(.x)))
```

make sure to pass .x otherwise it will not perform action on columns

`Note` : we have missed the column names above

`Adding column names`

```{r}
gapminder %>% map_df(~data.frame(class = class(.x),
                                 distinct = n_distinct(.x)),
                     .id = "column_name")
```

defining .x

```{r}
data.frame(n_distinct = n_distinct(gapminder %>% pluck(1)),
           class = class(gapminder %>% pluck(1)))
```

```{r}
continent_year <- gapminder %>% distinct(continent, year)
continent_year
```


```{r}
continents <- continent_year %>% 
                pull(continent) %>% 
                as.character

years <- continent_year %>% 
            pull(year)
```


```{r}
gapminder %>% 
  filter(continent == continents[1],
         year == years[1]) %>% 
  
  ggplot() +
  geom_point(aes(x = gdpPercap, y = lifeExp, col = country)) +
  ggtitle(paste(continents[1], years[1]))
```

```{r}
.x <- continents[1]
.y <- years[1]
  
gapminder %>% 
  filter(continent == .x,
         year == .y) %>% 
  
  ggplot() +
  geom_point(aes(x = gdpPercap, y = lifeExp, col = country)) +
  ggtitle(paste(.x, .y))
```

Applying above test code for generic usage object

```{r}
plot_list <- map2(.x = continents, 
                  .y = years,
     .f = ~{gapminder %>% 
  filter(continent == .x,
         year == .y) %>% 
  
  ggplot() +
  geom_point(aes(x = gdpPercap, y = lifeExp, col = country)) +
  ggtitle(paste(.x, .y))
       })
```


```{r}
plot_list[1]
```

```{r}
plot_list[[22]]
```

Below I nest the gapminder data by continent.

```{r}
gapminder_nested <- gapminder %>% 
                      group_by(continent) %>% 
                      nest()

gapminder_nested
```

```{r}
gapminder_nested %>% unnest()
```


```{r}
gapminder_nested$data[[1]]
```

```{r}
gapminder_nested$data[[2]]
```


To pull or extract from it by index

```{r}
gapminder_nested %>% 
  pluck(1)
```

To pull or extract data from it by index

```{r}
gapminder_nested %>% 
  pluck("data",1)
```


```{r}
tibble(list_col = list(c(1, 5, 7),
                       5,
                       c(10, 10, 11))) %>% 
    mutate(list_sum = map(.x = list_col, .f = sum))
```

since map returns a lits itself, so we will need to pull from the list

```{r}
tibble(list_col = list(c(1, 5, 7),
                       5,
                       c(10, 10, 11))) %>% 
    mutate(list_sum = map(.x = list_col, .f = sum)) %>% 
  pull(list_sum)
```

it could be better to result out a ve tor instead of list

```{r}
tibble(list_col = list(c(1, 5, 7),
                       5,
                       c(10, 10, 11))) %>% 
  mutate(list_sum = map_dbl(.x = list_col, .f = sum))
```

How to get mean from column listed tibble data

```{r}
.x <- gapminder_nested %>% 
        pluck("data", 1)
```


```{r}
mean(.x$lifeExp)
```
Now applying mean function on all column listed tible data

```{r}
gapminder_nested %>% 
  mutate(avg_lifeExp = map_dbl(data, ~{mean(.x$lifeExp)}))
```

### fitting a linear model for each contines / row

```{r}
gapminder_nested <- gapminder_nested %>% 
  mutate(lm_obj = map(data, ~lm(lifeExp ~ pop + gdpPercap + year, data = .x)))

gapminder_nested
```

#### checking linear model for first continent

```{r}
gapminder_nested %>% pluck("lm_obj", 1)
```

### Adding Predictions

```{r}
gapminder_nested <- gapminder_nested %>% 
  mutate(pred = map2(.x = lm_obj, .y = data, function(.x,.y) predict(.x, .y)))

gapminder_nested
```

can also be written as 

```{r}
gapminder_nested %>% 
  mutate(pred = map2(lm_obj, data, function(.lm, .data) predict(.lm, .data)))

```


#### Calc. correlation pred reps. vs true resp.

```{r}
gapminder_nested <- gapminder_nested %>% 
  mutate(cor = map2_dbl(pred, data, function(.pred, .data) cor(.pred, .data$lifeExp)))

gapminder_nested
```

```{r}
gapminder %>% 
  group_by(continent) %>% 
  nest %>% 
  mutate(lm_obj = map(data, ~lm(lifeExp ~ pop + year + gdpPercap, data = .))) %>% 
  mutate(lm_tidy = map(lm_obj, broom::tidy))
```


```{r}
gapminder %>% 
  group_by(continent) %>% 
  nest %>% 
  mutate(lm_obj = map(data, ~lm(lifeExp ~ pop + year + gdpPercap, data = .))) %>% 
  mutate(lm_tidy = map(lm_obj, broom::tidy)) %>% 
  ungroup() %>% 
  transmute(continent, lm_tidy) %>% 
  unnest(cols = c(lm_tidy))
```


### split function

this will split the data frame on basisi of factors provided from the variable

```{r}
gapminder %>% split(gapminder$continent)
```


```{r}
set.seed(23489)

gapminder_list <- gapminder %>% 
  split(gapminder$continent) %>% 
  map(~sample_n(., 5))

gapminder_list
```


### keep()

function to limit/ filter data frame with conditions

discar() is opposite of keep

```{r}
gapminder_list %>% 
  keep(~{mean(.x$lifeExp) > 70})
  
```


### Reduce()

`reduce()` is designed to combine (reduces) all of the elements of a list into a single object by iteratively applying a binary function (a function that takes two inputs).

```{r}
reduce(c(1, 2, 3), sum)
```

### accumulate()

also returns the intermediate values.

```{r}
accumulate(c(1, 2, 3), sum)
```

`Reduce` can be useful in combining columns by using left_join etc. or to do repeated `rbind()`

```{r}
gapminder_list %>% 
  reduce(rbind)
```



### Logical statements for lists

`every()`, `some()`

For instance to ask whether every continent has average life expectancy greater than 70, you can use every()

```{r}
gapminder_list %>% every(~{mean(.x$life) > 70 })
```


```{r}
gapminder_list %>% some(~{mean(.x$life) > 70})
```


### has_element()

this is equivalent of %in%

```{r}
list(1, c(2, 5, 1), "a") %>% has_element("a")
```















































