---
title: "Hands-on dplyr tutorial"
output: 
  html_notebook:
    theme: spacelab
    highlight: tango
    df_print: paged
    toc: true
    toc_float: true
    number_sections: true
    toc_depth: 4
  pdf_document:
    toc: true
    toc_depth: 4    
---


# Dplyr Practice for Data Wrangling

from: https://www.youtube.com/watch?v=jWjqLW-u3hc


## Loading necesary libs & data

### Loading functionaity & dataset lib

```{r}
# install.packages("tidyverse")
# install.packages("hflights")

library(tidyverse)
library(hflights)
```


```{r}
data(hflights)
```


```{r}
head(hflights)
```

```{r}
str(hflights)
```

```{r}
summary(hflights)
```


```{r}
class(hflights)
```
## Creating tibble / local data frame

```{r}
flights <- as_tibble(hflights)
class(flights)
```


I am skipping on all basic dply work that I am pretty comfortable with, so please refer to video if you want to practice every bit of dplyr


```{r}
filter(flights, Month == 1, DayofMonth == 1)
```


```{r}
filter(flights, UniqueCarrier %in%  c("AA","AS"))
```

### Creating variables on fly without saving it with mutate()

```{r}
flights %>% 
  select(Distance, AirTime) %>% 
  mutate(Speed = Distance / AirTime * 60 )
```


Create a table grouped by Dest, & then take mean of Arrdelay for each group

```{r}
flights %>% 
  # select(Dest, ArrDelay) %>% 
  group_by(Dest) %>% 
  summarise(ArrDelay_mean = mean(ArrDelay, na.rm = T))
```


#### summarise_each (also mutate_each also available)

for each carrier calculate percentage of flights canceled or diverted
```{r}

flights %>% 
  group_by(UniqueCarrier) %>% 
  summarise_each(funs(mean), Cancelled, Diverted)
  
```


find out the flight which gets affected the most in terms of canceled and diversion

```{r}
flights %>% 
  group_by(UniqueCarrier) %>% 
  summarise_each(funs(mean), Cancelled, Diverted) %>% 
  mutate(problem_flight_percent = (Cancelled + Diverted)) %>% 
  arrange(desc(problem_flight_percent))
```


for each carrier, calculate the minimum and maximum arrival and departure delays 

```{r}
flights %>% 
  group_by(UniqueCarrier) %>% 
  summarise_each(funs(min(., na.rm = T), max(., na.rm = T) ), matches("Delay", ignore.case = T) ) 
```

for each day of the year, count the total number of flights and sort in ascending order

```{r}
flights %>% 
  group_by(Month, DayofMonth) %>% 
  summarise(flights_count = n()) %>% 
  arrange(desc(flights_count))
```


above same code can be rewritten with tally

```{r}
flights %>% 
  group_by(Month, DayofMonth) %>% 
  tally(sort = TRUE)
  
```


for each destination, count total number of flights and number of distinct flights that flew there

```{r}
flights %>% 
  group_by(Dest) %>% 
  summarise(tot_flights = n(), tot_distinct_flights = n_distinct(TailNum, na.rm = TRUE))
```


for each destination show number of canceled and non canceled flights

```{r}
flights %>% 
  group_by(Dest) %>% 
  select(Dest, Cancelled) %>% 
  table() %>% head()
```


### window functions

#### longest departure delays

for each carriers calculate which two days of the year they had their longest departure delays.
smallest values is ranked as rank 1, so use desc to rank by largest values

```{r}
flights %>% 
  group_by(UniqueCarrier) %>% 
  select(Month, DayofMonth, DepDelay) %>% 
  mutate(rank = rank(desc(DepDelay))) %>% 
  filter(rank <= 2) %>% 
  arrange(UniqueCarrier, desc(DepDelay))
```


above code can be written without creating rank variable in mutate()

```{r}
flights %>% 
  group_by(UniqueCarrier) %>% 
  select(Month, DayofMonth, DepDelay) %>% 
  filter(rank(desc(DepDelay)) <= 2) %>% 
  arrange(UniqueCarrier, desc(DepDelay))
```


this code can further be improved with `top_n()` function as top_n replaces the rank function

```{r}
flights %>% 
  group_by(UniqueCarrier) %>% 
  select(Month, DayofMonth, DepDelay) %>% 
  top_n(n = 2, wt = DepDelay) %>% 
  arrange(UniqueCarrier, desc(DepDelay))
```


#### change of number of flights

for each month, calculate number of flights and changes from previous month

```{r}
flights %>% 
  group_by(Month) %>% 
  summarise(flight_count = n()) %>% 
  mutate(mom_change = flight_count - lag(flight_count))
```


above code can be written using tally function as tally simply replaces n() within summarise()


```{r}
flights %>% 
  group_by(Month) %>% 
  tally() %>% 
  mutate(mom_change = n - lag(n))
```



### other useful functions


```{r}
flights %>% 
  sample_n(15)
```


```{r}
flights %>% sample_frac(.05)
```


```{r}
glimpse(flights)
```























