---
title: "For loop testing - Unemployment EDA"
output: 
  html_notebook:
    highlight: tango
    df_print: paged
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    number_sections: yes
    toc_depth: 6
  html_document:
    toc: yes
    toc_depth: '6'
    df_print: paged
---

# Options & libs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, results='hide', fig.keep='all', dpi = 300, out.width = "100%",attr.output='style="max-height: 300px;"')
```

CSS for scrollable output & Header colors

```{css, echo=FALSE}
.scroll-100 {
  max-height: 100px;
  overflow-y: auto;
  background-color: inherit;
}

```

Turning scientific / Exponential numbers off

```{r}
options(scipen = 999)
```

```{r}
library(tidyverse)
library(tidytuesdayR)
library(ggthemes)
library(glue)
library(scales)
```

Creating & setting custom theme

```{r}

theme_viny_bright <- function(){
  
  library(ggthemes)
  
  ggthemes::theme_fivethirtyeight() %+replace%
  
  theme(
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 8),
    legend.text = element_text(size = 7),
    panel.background = element_rect(fill = "white"),
    plot.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    legend.background = element_rect(fill = NA),
    legend.key = element_rect(fill = NA),
    plot.title = element_text(hjust = 0.5,
                              size = 16,
                              face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 10, face = "bold"),
    plot.caption = element_text(hjust = 1, size = 8)
      )
  
  }

theme_set(theme_viny_bright())
```

**sources:**

Inspired from: <https://www.youtube.com/watch?v=gkZ5n8sfXns>

# Loading data

```{r}
tt <- tt_load("2021-02-23")
tt
```

# EDA

```{r}
employed <- tt$employed
employed
```

```{r}
str(employed)
```

```{r}
summary(employed)
```

```{r}
employed %>% 
  mutate_if(is.character, as.factor) %>% 
  summary()
```

looks like we have NA's in data

## Missing Values

```{r}
sapply(employed, function(x) sum(is.na(x))) %>% 
  as.data.frame()
```

```{r}
library(naniar)
```

```{r}
employed %>% 
  naniar::gg_miss_upset()
```

## Cols Freq

```{r}
table(employed$industry) %>% 
  as.data.frame() %>% 
  arrange(desc(Freq)) %>% 
  
  ggplot(aes(Freq, fct_reorder(Var1, Freq), fill = Var1))  +
  geom_col() +
  theme(legend.position = "none")
```

```{r}
top_freq_elements <- function(x){
  
  table(x) %>% 
    as.data.frame() %>% 
    arrange(desc(Freq)) %>% 
    
    ggplot(aes(Freq, fct_reorder(x, Freq), fill = x))  +
    geom_col() +
    theme(legend.position = "none")
}
```

```{r}
employed %>% 
  select_if(is.character) %>% 
  map(., .f = top_freq_elements)
```

```{r}
employed %>% 
  count(year)
```

```{r}
employed %>% 
  count(industry) %>% 
  ggplot(aes(x = n, y = industry, fill = industry)) +
  geom_col() +
  theme(legend.position = "none")
```

```{r}
for (var_selected in names(employed)){
  employed %>% 
    count(.data[[var_selected]]) %>% 
    
    ggplot(aes(x = n, y = .data[[var_selected]], fill = .data[[var_selected]])) +
    geom_col() +
    theme(legend.position = "none") %>% 
    
    print()
  
  # employed %>% 
  # count(var_selected) %>% 
  # ggplot(aes(x = n, y = var_selected, fill = var_selected)) +
  # geom_col() +
  # theme(legend.position = "none")
}
```



from: onenote:///\\VINY-PC\Users\viny\Documents\OneNote%20Notebooks\R%20Learning%20&%20Notes\R%20Visualization.one#count()%20%20plot%20frequency%20of%20each%20variable%20in%20a%20function&section-id={C245D183-2D71-46D1-BCBE-2C1A047C220B}&page-id={FEB1F723-D8B8-4DB8-9BA3-ACD8DF96F454}&object-id={A46CDF35-1F4D-45E3-A63B-A89DC402039A}&10

```{r}
dummy_df <- data.frame(gender_vector = c("Male", "Female", "Female", "Male", "Male"),
                          color_vector = c('blue', 'red', 'green', 'white', 'black'),
                       num_vector = c(1,2,3,4,5)
) 

dummy_df
```


```{r}
sel_char_cols_fn <- function(df){
  df %>% 
    select_if(is.character) %>%
    head()
}

sel_char_cols_fn(dummy_df)
```

`select_if()` is working in above code

```{r}
count_char_cols_fn <- function(df,selected_var){
  df %>% 
    select_if(is.character) %>%
    count(.data[[selected_var]])
}

purrr::map(df = dummy_df, 
           .x = names(dummy_df %>%
                        select_if(is.character)),
           .f = count_char_cols_fn)
```

In above code we had to `select_if` in `map()` because it is applying `count()` var by var and if we would pass a unknown/numeric var to count function then it will not match

```{r}
dummy_df %>% 
  # select(gender_vector) %>%
  # as_data_frame() %>%
  count(gender_vector)
```

```{r}
dummy_df %>%
  as_tibble() %>% 
  select(gender_vector) %>%
  # as_data_frame() %>%
  count(gender_vector)
```

```{r}
employed %>%
  # as_tibble() %>% 
  # select(industry) %>%
  # as_data_frame() %>%
  count(industry)
```

```{r}
count_char_cols_fn2 <- function(df,selected_var){
  df %>% 
    if_else(class(.data[[selected_var]]) == "character",
            count(.data[[selected_var]]),
    )
}

purrr::map(df = dummy_df, 
           .x = names(dummy_df),
           .f = count_char_cols_fn2)
```

```{r}
class(dummy_df$gender_vector)
```

from: https://stackoverflow.com/questions/66516774/how-to-write-if-else-condition-within-a-function-in-r-and-then-apply-on-all-vari

```{r}
count_char_cols_fn2 <- function(df,selected_var){
    if_else(class(df[[selected_var]]) == "character",
            count(df, .data[[selected_var]]),
            )
}

purrr::map(df = dummy_df, 
           .x = names(dummy_df),
           .f = count_char_cols_fn2)
```

```{r}
count_char_cols_fn2 <- function(df,selected_var){
    if(class(df[[selected_var]]) == "character")
            count(df, .data[[selected_var]])
            
}

purrr::map(df = dummy_df, 
           .x = names(dummy_df),
           .f = count_char_cols_fn2)
```



```{r}
count_char_cols_fn2 <- function(df,selected_var){
    if(is.character(df[[selected_var]]) )
            count(df, .data[[selected_var]])
            
}

purrr::map(df = dummy_df, 
           .x = names(dummy_df),
           .f = count_char_cols_fn2)
```


```{r}
count_char_cols_fn2 <- function(df,selected_var){
    if(is.character(df[[selected_var]]) )
      count(df, .data[[selected_var]]) %>%
    
    ggplot(aes(x = n, y = .data[[selected_var]], fill = .data[[selected_var]]))+
    geom_col(show.legend = FALSE)
}

purrr::map(df = dummy_df, 
           .x = names(dummy_df),
           .f = count_char_cols_fn2)
```


