---
title: "tidyduesday from David Robinson"
output: 
  html_notebook:
    highlight: tango
    df_print: paged
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: false
    number_sections: false
    toc_depth: 6
---


# Ikea furniture

## options & settings


chunk options

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, dpi = 300, out.width = "100%",attr.output='style="max-height: 300px;"')
```


CSS for scrollable output & Header colors 

```{css, echo=FALSE}
.scroll-100 {
  max-height: 100px;
  overflow-y: auto;
  background-color: inherit;
}

tbody tr:hover {
  background: #dddddd;
}


h1, #TOC>ul>li {
  color: #B64D3A;
}

h2, #TOC>ul>ul>li {
  color: #000000;
}

h3, #TOC>ul>ul>ul>li {
  color: #643cb2;
}

h4, #TOC>ul>ul>ul>ul>li {
  color: #ae0058;
}

h5, #TOC>ul>ul>ul>ul>ul>li {
  color: #ffa447;
}

h6, #TOC>ul>ul>ul>ul>ul>ul>li {
  color: #DAE3D9;
}

```

Turning scientific / Exponential numbers off

```{r}
options(scipen = 999)
```


## Source

https://www.youtube.com/watch?v=lY0YLDZhT88&t=389s


## Loading libs

```{r}
library(tidyverse)
library(ggthemes)

library(tidytuesdayR)
```


## Creating & setting custom theme

```{r}

theme_viny_bright <- function(){
  
  library(ggthemes)
  
  ggthemes::theme_fivethirtyeight() %+replace%
  
  theme(
    axis.title = element_text(),
    
    axis.text = element_text(size = 13),
    
    legend.text = element_text(size = 10),
    
    panel.background = element_rect(fill = "white"),
    
    plot.background = element_rect(fill = "white"),
    
    strip.background = element_blank(),
    
    legend.background = element_rect(fill = NA),
    
    legend.key = element_rect(fill = NA),

    plot.title = element_text(hjust = 0.5,
                              size = 19,
                              face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, colour = "maroon")
      )
  
  }

theme_set(theme_viny_bright())
```


## Loading data

```{r}
tt <- tidytuesdayR::tt_load("2020-11-03")
```

```{r}
tt$ikea %>% head()
```


```{r}
ikea <- tt$ikea %>% 
  select(-X1)

str(ikea)
```

## Data Exploration 

### Missing data

```{r}
colSums(is.na(ikea))
```

### Missing data "?"

```{r}

element_freq <- function(x){
  
  return(table(x)[names(table(x)) == "?"])

  }
  
```


```{r}
ikea %>% map(., .f= element_freq) 
```

### Missing data "-"

```{r}

element_freq <- function(x){
  
  return(table(x)[names(table(x)) == "-"])

  }
  
```


```{r}
ikea %>% map(., .f= element_freq) 
```

### Distinct counts in each col

```{r}
ikea %>% summarise_all(n_distinct)
```

```{r}
ikea %>% 
  count(category, sort = TRUE)
```

### count of items category wise

```{r}
ikea %>% 
  count(category) %>% 
  mutate(category = fct_reorder(category, n)) %>% 
  ggplot(aes(x = category, y = n)) +
  geom_col() +
  coord_flip()
```

### Price variation in each category

```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(x = category, y = price)) +
  geom_boxplot() +
  coord_flip()
```

```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(x = category, y = price)) +
  geom_boxplot() +
  coord_flip() +
  scale_y_log10()
```

```{r fig.width=8, fig.height=8 }
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(x = category, y = price)) +
  geom_boxplot() +
  geom_jitter(width = 0, height = .1) +
  coord_flip() +
  scale_y_log10()
```


### Adding category count

```{r fig.width=8, fig.height=8 }
library(glue)

ikea %>%
  add_count(category, name = "category_total") %>% 
  mutate(
    category = glue("{category } ({category_total})"),
    category = fct_reorder(category, price)) %>% 
  ggplot(aes(x = category, y = price)) +
  geom_boxplot() +
  geom_jitter(width = 0, height = .1) +
  coord_flip() +
  scale_y_log10()
```


```{r fig.width=8, fig.height=8 }
library(glue)

ikea %>%
  add_count(category, name = "category_total") %>% 
  mutate(
    category = glue("{category } ({category_total})"),
    category = fct_reorder(category, price)) %>% 
  ggplot(aes(x = category, y = price)) +
  geom_boxplot() +
  # geom_jitter(width = 0, height = .1) +
  coord_flip() +
  scale_y_log10()
```



```{r fig.width=8, fig.height=8 }
library(ggridges)

ikea %>%
  add_count(category, name = "category_total") %>% 
  mutate(
    category = glue("{category } ({category_total})"),
    category = fct_reorder(category, price)) %>% 
  ggplot(aes(y = category, x = price)) +
  geom_density_ridges() +
  # geom_jitter(width = 0, height = .1) +
  # coord_flip() +
  scale_x_log10()
```


```{r fig.width=8, fig.height=8 }

ikea %>%
  add_count(category, name = "category_total") %>% 
  mutate(
    category = glue("{category } ({category_total})"),
    category = fct_reorder(category, price)) %>% 
  ggplot(aes(y = category, x = price)) +
  geom_density_ridges()
  # geom_jitter(width = 0, height = .1) +
  # coord_flip() +
  # scale_x_log10()
```


```{r fig.width=8, fig.height=8 }

ikea %>%
  add_count(category, name = "category_total") %>% 
  mutate(
    category = glue("{category } ({category_total})"),
    category = fct_reorder(category, price)) %>% 
  ggplot(aes(y = category, x = price, fill = other_colors, alpha = .25)) +
  geom_density_ridges() +
  # geom_jitter(width = 0, height = .1) +
  # coord_flip() +
  scale_x_log10()
```


```{r fig.width=8, fig.height=8 }

ikea %>%
  add_count(category, name = "category_total") %>% 
  mutate(
    category = glue("{category } ({category_total})"),
    category = fct_reorder(category, price)) %>% 
  ggplot(aes(x = category, y = price, fill = other_colors)) +
  geom_boxplot() +
  # geom_jitter(width = 0, height = .1) +
  coord_flip() +
  scale_y_log10()
```

```{r fig.width=8, fig.height=8 }

ikea %>%
  add_count(category, name = "category_total") %>% 
  mutate(
    category = glue("{category } ({category_total})"),
    category = fct_reorder(category, price)) %>% 
  ggplot(aes(x = category, y = price)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, height = .1, aes(color = other_colors), alpha = 0.5) +
  coord_flip() +
  scale_y_log10()
```

### popular names by catgories

```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  count(name, category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n)) %>% 
  ggplot(aes(x = n, y = name, fill = category)) +
  geom_col()
```


```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  filter(name != "Other") %>% 
  count(name, category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n)) %>% 
  ggplot(aes(x = n, y = name, fill = category)) +
  geom_col()
```


```{r}
ikea %>% 
  mutate(name = fct_lump(name, 21)) %>% 
  filter(name != "Other") %>% 
  count(name, category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n, sum)) %>% 
  ggplot(aes(x = n, y = name, fill = category)) +
  geom_col() +
  theme_light()
```


```{r}
# setting legend order

ikea %>% 
  mutate(name = fct_lump(name, 21)) %>% 
  filter(name != "Other") %>% 
  count(name, category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n, sum)) %>% 
  ggplot(aes(x = n, y = name, fill = category)) +
  geom_col() +
  theme_light() +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE))
```


```{r}
# categories on y-axis & 

ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  filter(name != "Other") %>%
  count(name, category, sort = TRUE) %>% 
  mutate(category = fct_reorder(category, n, sum)) %>% 
  ggplot(aes(x = n, y = category, fill = name)) +
  geom_col() +
  theme_light() +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE))
```
















